Bioverse: Origins of Life

### 2024-07-13 src/tex/ms.tex
remove O2 as biosignature text

% detecting methanogenic life: Sandora2020, Wang2018, Seeburger2023
A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
No individual component of an atmosphere has been identified as a reliable biosignature in isolation~\citep{Seager2016}, and the detection of Oxygen alone will certainly not be sufficient to confirm the presence of life.
Nevertheless, we focus here on detecting this key absorber as it represents the general inherent observational challenges and trends.

>>>>

% detecting methanogenic life: Sandora2020, Wang2018, Seeburger2023
% TODO: IF SPECIFIC BIOSIGNATURE: use:
%A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
%No individual component of an atmosphere has been identified as a reliable biosignature in isolation~\citep{Seager2016}, and the detection of Oxygen alone will certainly not be sufficient to confirm the presence of life.
%Nevertheless, we focus here on detecting this key absorber as it represents the general inherent observational challenges and trends.
